### 2018-10-16 journal/ms.Rmd
new journal

data_long <- data_all %>%
  rename(Sem = sem_deg, Phono=phono_deg) %>%
  gather(predictor, value, Sem:frequency) %>%
  filter(predictor == "Sem" | predictor == "Phono")

@@

plot_correlation_comp <- ggplot(subset(data_long, measure == "understands"), aes(x=value, y=aoa))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="understands"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age")

@@

@@

plot_growth_preds_prod <- ggplot(subset(growth_preds, measure == "produces"), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

plot_growth_preds_comp <- ggplot(subset(growth_preds, measure == "understands"), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

@@

```{r growthPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Evaluation of network growth scenarios, for both A) production and B) comprehension. We plot values when predictors are evaluted individually (dotted), and when combined in the same growth model (solid). Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals). Positive values mean that learning proceeds according to the predictions of the growth scenario. Negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}

legend <- get_legend(plot_growth_preds_prod)

plot_noLegend <- plot_grid(plot_growth_preds_prod + theme(legend.position="none"), NULL, plot_growth_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))

@@

@@

```{r}
static_preds <- feather::read_feather("../saved_data/static_preds.feather")

plot_static_preds_prod <- ggplot(subset(static_preds, measure =="produces"), aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test), 
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=5)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

plot_static_preds_comp <- ggplot(subset(static_preds, measure =="understands"), aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=5)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

@@

```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of predictor coefficients by language in production (A) and comprehension (B), with ranges indicating 95\\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA)."}

legend <- get_legend(plot_static_preds_prod)

plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))

#plot_static_preds_prod

### What is the relative contribution of each growth model?

@@

@@

@@

## Does the network's effect change with age?

As a final analysis, we examined  whether the effect of semantic and phnonological networks change over development. @braginsky2016 found that

>>>>

data_long <- data_all %>%
  rename(Sem = sem_deg, Phono=phono_deg) %>%
  gather(predictor, value, Sem:frequency) %>%
  dplyr::filter(predictor == "Sem" | predictor == "Phono")

@@

plot_correlation_comp <- ggplot(subset(data_long, measure == "understands" & aoa < 35), aes(x=value, y=aoa))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="understands"), aes(label=paste("r=", cor, sep="")), x=3.5, y=25, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age")

@@

<!--

@@

plot_growth_preds_prod <- ggplot(subset(growth_preds, measure == "produces" & Test=='Individual'), aes(x = model , y = mean)) +
  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7) + #,+
        #axis.text.x = element_text(size=7.5, angle=45)) +
  scale_y_continuous(breaks =c(0,0.2))
  #scale_y_discrete(breaks =NULL)

plot_growth_preds_comp <- ggplot(subset(growth_preds, measure == "understands" & Test=='Individual'), aes(x = model , y = mean)) +
  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7) +
  scale_y_continuous(breaks =c(0,0.2))

@@

-->

```{r}
##Test
growth_preds <- feather::read_feather("../saved_data/growth_preds.feather")

growth_preds$model <- plyr::mapvalues(growth_preds$model, 
                                 from = c("semPAC","semPAT","phonoPAC", "phonoPAT"), 
                                 to = c("semEXT","semINT","phonoEXT", "phonoINT"))

growth_preds$measure <- plyr::mapvalues(growth_preds$measure, 
                                 from = c("produces","understands"), 
                                 to = c("production","comprehension"))

plot_growth_preds <- ggplot(subset(growth_preds, Test=='Individual'), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=measure),
  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7) + #,+
        #axis.text.x = element_text(size=7.5, angle=45)) +
  scale_y_continuous(breaks =c(0,0.2))  +
  #scale_y_discrete(breaks =NULL)
  ylab("Estimate") +xlab("Mechanism")

#plot_growth_preds
```

```{r growthPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Evaluation of growth scenarios (EXT: externally-driven, INT: internally-driven) for both semantic and phonological networks. Each point represents the mean of the posterior distribution of the growth parameter, with ranges representing 95\\% credible intervals. Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}

#legend <- get_legend(plot_growth_preds_prod)

#plot_noLegend <- plot_grid(plot_growth_preds_prod + theme(legend.position="none"), NULL, plot_growth_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

#plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))

#plot_noLegend <- plot_grid(plot_growth_preds_prod, NULL, plot_growth_preds_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

#plot_grid(plot_noLegend)

@@

plot_growth_preds

@@

```{r}
##Test
static_preds <- feather::read_feather("../saved_data/static_preds.feather")

static_preds$predictor <- plyr::mapvalues(static_preds$predictor, 
                                 from = c("sem_deg","phono_deg","frequency", "length"), 
                                 to = c("semEXT","phonoEXT", "frequency", "length"))

static_preds$measure <- plyr::mapvalues(static_preds$measure, 
                                 from = c("produces","understands"), 
                                 to = c("production","comprehension"))

plot_static_preds <- ggplot(subset(static_preds, Test=='Combined'), aes(x = predictor , y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., col = predictor, linetype=measure),
  #geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7) + #,+
        #axis.text.x = element_text(size=7.5, angle=45)) +
  scale_y_continuous(breaks =c(0,0.2))  +
  #scale_y_discrete(breaks =NULL)
  ylab("Estimate") +xlab("Mechanism")

plot_static_preds

```
<!--
```{r}
static_preds <- feather::read_feather("../saved_data/static_preds.feather")

plot_static_preds_prod <- ggplot(subset(static_preds, measure =="produces" & Test =="Combined"), aes(x = predictor, y = estimate)) +
  #geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test), 
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=5)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

plot_static_preds_comp <- ggplot(subset(static_preds, measure =="understands" & Test =="Combined"), aes(x = predictor, y = estimate)) +
  #geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test),
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=5)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

```
-->

```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of the relative contribution of each predictor of AoA in the combined regression model. Results are shown for both production and comprehension data. Ranges indicate 95\\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA)."}

#legend <- get_legend(plot_static_preds_prod)

#plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

#plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))

#plot_noLegend <- plot_grid(plot_static_preds_prod, NULL, plot_static_preds_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

#plot_grid(plot_noLegend)

plot_static_preds

@@

<!--
### What is the relative contribution of each growth model?

@@

static_preds_all$predictor <- plyr::mapvalues(static_preds_all$predictor, 
                                 from = c("sem_deg","phono_deg","frequency", "length"), 
                                 to = c("semEXT","phonoEXT","frequency", "length"))

@@

-->

@@

### 2018-10-16 journal/ms.tex
new journal

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Word Learning as Network Growth: A Cross-linguistic Analysis},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/growthPred-1} \caption{Evaluation of network growth scenarios, for both A) production and B) comprehension. We plot values when predictors are evaluted individually (dotted), and when combined in the same growth model (solid). Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals). Positive values mean that learning proceeds according to the predictions of the growth scenario. Negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:growthPred}
\end{figure}

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPred-1} \caption{Estimates of predictor coefficients by language in production (A) and comprehension (B), with ranges indicating 95\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).}\label{fig:staticPred}
\end{figure}

\subsubsection{What is the relative contribution of each growth
model?}\label{what-is-the-relative-contribution-of-each-growth-model}

Above we evaluated the network growth scenarios individually. As a next
step, we analyzed their relative contribution to the learning process.
This was done through adding more fitted parameters to the model, that
is, by substituting \(\beta d_i\) in formula (1) with:
\[\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}\]
where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and
PhonoPAC. Using the same fitting technique, we obtained the values shown
in Figure \ref{fig:pred_ind}. PAC dominates the learning. Both
phonological and semantic networks contribute to lexical growth, but the
phonological network appears to be stronger and more consistent across
languages. In summary, the findings show that both semantic and
phonological networks contribute to the learning process, and that they
both grow primarily by PAC, relying on the external connectivity in the
learning environment, rather than the internal connectivity in the
acquired lexicon.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{figs/plot_static_preds_all} \caption{Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect for both production and comprehension. Ranges indicate 95\% confidence intervals. Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:staticAll}
\end{figure}

@@

\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/WordRec}}}
\vspace{1em}

>>>>

  \usepackage{graphicx}
  \makeatletter
  \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
  \def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
  \makeatother
  % Scale images if necessary, so that they will not overflow the page
  % margins by default, and it is still possible to overwrite the defaults
  % using explicit options in \includegraphics[width, height, ...]{}
  \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Word Learning as Network Growth: A Cross-linguistic Analysis},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/growthPred-1} \caption{Evaluation of growth scenarios (EXT: externally-driven, INT: internally-driven) for both semantic and phonological networks. Each point represents the mean of the posterior distribution of the growth parameter, with ranges representing 95\% credible intervals. Positive values mean that learning proceeds according to the predictions of the growth scenario, whereas negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:growthPred}
\end{figure}

@@

\includegraphics{ms_files/figure-latex/unnamed-chunk-6-1.pdf}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{ms_files/figure-latex/staticPred-1} \caption{Estimates of the relative contribution of each predictor of AoA in the combined regression model. Results are shown for both production and comprehension data. Ranges indicate 95\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).}\label{fig:staticPred}
\end{figure}

@@

\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
\vspace{1em}

### 2018-10-16 main_analyses.Rmd
new journal

#Save at this point
#feather::write_feather(data_growth, "saved_data/data_growth.feather")
#data_growth <- feather::read_feather("saved_data/data_growth.feather") 
```

>>>>

#Save at this point
#feather::write_feather(data_growth, "saved_data/data_growth.feather")
data_growth <- feather::read_feather("saved_data/data_growth.feather") 
```
